Spatial Analysis

### 2021-06-09 Scripts/spatial_analisis.Rmd
run analysis for bsb

  # --------------- #
  # Testing
  print(paste(yr))
  yr = 1976
  # --------------- #

@@

# Test me
# Needs variables in Control panel
# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)

lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])

@@

# Load interpolated data
historic_tif <- my_path("R","Partial","interpolated_data.csv",read = T)

@@

@@

total_fited <- historic_tif %>% 
  group_by(year,region) %>% 
  summarise(total_value = sum(value,na.rm=T))

state_fit <- historic_tif %>% 
  group_by(state,year,region) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100) %>% 
  left_join(periods) %>% 
  group_by(ID = state,period,region) %>% 
  summarise(mean_per = round(mean(percentage)))

@@

total_fited <- historic_tif %>% 
  group_by(year,region) %>% 
  summarise(total_value = sum(value,na.rm=T))

# group by state
state_fit <- historic_tif %>% 
  group_by(state,year,region) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100) %>% 
  group_by(state,region)

@@

# group by state
state_fit <- historic_tif %>% 
  group_by(state,year,region) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100) %>% 
  group_by(state,region) %>% 
  mutate(RMean = zoo::rollmean(x = percentage, 
                            10,
                            fill = NA,
                            na.rm=T)
    )

>>>>

  # --------------- #
  # Testing
  # print(paste(yr))
  # yr = 1976
  # --------------- #

@@

# Test me
# Needs variables in Control panel
# Test no data: "Alosa aestivalis", reg = "Northeast US Fall", yr = 1974 
# tis(input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = "Northeast US Fall", yr = 1973)

# lapply(years,tis,input_data = ocean_data, grid = grid_eez_df, taxa = "Illex illecebrosus", reg = regions[2])

@@

# Load interpolated data
# "Centropristis striata"
# 
historic_tif <- my_path("R","Partial/Interpolation","tif_Centropristis_striata.csv", read = T)

# Spatial data

@@

# print for notebook
head(historic_tif)
```

@@

total_fited <- historic_tif %>% 
  group_by(year,region) %>% 
  summarise(total_value = sum(value,na.rm=T),.groups = "drop")

state_fit <- historic_tif %>% 
  group_by(state,year,region) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100) %>% 
  left_join(periods) %>% 
  group_by(ID = state,period,region) %>% 
  summarise(mean_per = round(mean(percentage)),.groups = "drop")

@@

total_fited <- historic_tif %>% 
  group_by(year,region) %>% 
  summarise(total_value = sum(value,na.rm=T),.groups = "drop")

# group by state
state_fit <- historic_tif %>% 
  group_by(state,year,region) %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100)

@@

# group by state
state_fit <- historic_tif %>% 
  group_by(state,year,region,.groups = "drop") %>% 
  summarise(state_value = sum(value,na.rm= T), .groups = "drop") %>% 
  left_join(total_fited,
            by = c("year","region")) %>%
  mutate(percentage = state_value/total_value*100) %>% 
  group_by(state,region) %>% 
  mutate(RMean = zoo::rollmean(x = percentage, 
                            10,
                            fill = NA,
                            na.rm=T)
    )
